---
title: "Model Details for example_package"
author: "Jane Doe"
date: "2016-11-08"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Model Details for example_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Coursera)
```

```{r}
my_vec <- 1:10
```


#' Print "Hello world" 
#'
#' This is a simple function that, by default, prints "Hello world". You can 
#' customize the text to print (using the \code{to_print} argument) and add
#' an exclamation point (\code{excited = TRUE}).
#'
#' @param to_print A character string giving the text the function will print
#' @param excited Logical value specifying whether to include an exclamation
#'    point after the text
#' 
#' @return This function returns a phrase to print, with or without an 
#'    exclamation point added. As a side effect, this function also prints out
#'    the phrase. 
#'
#' @examples
#' hello_world()
#' hello_world(excited = TRUE)
#' hello_world(to_print = "Hi world")
#'
#' @export
hello_world <- function(to_print = "Hello world", excited = FALSE){
    if(excited) to_print <- paste0(to_print, "!")
    print(to_print)
}
